---
title: "ass1"
author: "me"
date: "November 20, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



##pull the train out

```{r}
df_train<-read.csv(unz("./Titanic.zip","Titanic/train.csv"),sep=",")
```


#Preprocessing

##take out the title from the name (mr./miss./Dr.) and make it a field and make it a factor

```{r}
df_train$Name<-as.factor(sapply(df_train$Name,function(x) substr(x,gregexpr(pattern =',',x)[[1]][1]+2,gregexpr(pattern ='\\.',x)[[1]][1]+1)))
```

##makr survive a factor

```{r}
df_train$Survived<-as.factor(df_train$Survived)
```

##turn the nulls in "Embarked" into the string "missing"

```{r}
levels(df_train$Embarked)[1]="missing"

for(i in 1:length(df_train$Age)){
  if(is.na(df_train$Age[i]))
    df_train$Age[i] <- mean(df_train$Age, na.rm = TRUE)
}
```

##delete the passengerID, the Cabin and the Ticket
### we deleted the cabin after we ran ImpVar

```{r}
df_train<-subset(df_train,select = -c(PassengerId,Cabin,Ticket))
```


#algorithms

##c50

###pull the libraries
```{r}
#install.packages("caret")
library(caret)
#install.packages("C50")
library(C50)

#install.packages("e1071")
library(e1071)
```

###set seed
```{r}
set.seed(123)
```

###create control the uses cross validation with k=10
```{r}
control <- trainControl(method="cv", number=10)
```

##tuning

###we tune the winnow and the model
```{r}
grid <- expand.grid(.winnow = c(TRUE,FALSE),.trials=30, .model=c('tree','rules'))
fit.c50 <- train(Survived~., data=df_train, method="C5.0", metric="Accuracy", trControl=control,tuneGrid =grid,na.action=na.pass)
```

### plot

```{r}
plot(fit.c50)
```



##xgb

###set seed
```{r}
set.seed(123)
```

###create control the uses cross validation with k=10
```{r}
control <- trainControl(method="cv", number=10)
```

##tuning

###we tune the winnow and the model
```{r}
grid <- expand.grid(.nrounds=10,.max_depth=6,.eta=c(0.1,0.2,0.3),.gamma=0.1,.colsample_bytree=c(0.5,0.6,0.7),.min_child_weight=0.1,.subsample=0.75)
fit.xgb <- train(Survived~., data=df_train, method="xgbTree",  trControl=control, verbose=FALSE,tuneGrid =grid,na.action=na.pass)
```

### plot

```{r}
plot(fit.xgb)
```



##random forest

###set seed
```{r}
set.seed(123)
```

###create control the uses cross validation with k=10
```{r}
tc <- trainControl(method="cv", number=3)
```

##tuning

###we tune the winnow and the model
```{r}
Grid <- expand.grid(.mtry = c(4:16))
fit.rf <- train(Survived~., data=df_train , method='rf', trControl=tc,tuneGrid=Grid,metric='Accuracy',na.action = na.pass)
```

### plot

```{r}
plot(fit.rf)
```


#print the result of the test into a file for the web


```{r}

df_test<-read.csv(unz("./Titanic.zip","Titanic/test.csv"),sep=",")

pid<-df_test$PassengerId

df_test$Name<-as.factor(sapply(df_test$Name,function(x) substr(x,gregexpr(pattern =',',x)[[1]][1]+2,gregexpr(pattern ='\\.',x)[[1]][1]+1)))


levels(df_test$Cabin)[1]="missing"
levels(df_test$Embarked)[1]="missing"

for(i in 1:length(df_test$Age)){
  if(is.na(df_test$Age[i]))
    df_test$Age[i] <- mean(df_test$Age, na.rm = TRUE)
}


for(i in 1:length(df_test$Fare)){
  if(is.na(df_test$Fare[i]))
    df_test$Fare[i] <- mean(df_test$Fare, na.rm = TRUE)
}

df_test<-subset(df_test,select = -c(PassengerId,Cabin,Ticket))

fit.rf$xlevels[["Cabin"]]<-union(fit.rf$xlevels[["Cabin"]],levels(df_test$Cabin))
fit.rf$xlevels[["Name"]]<-union(fit.rf$xlevels[["Name"]],levels(df_test$Name))


res<-predict(fit.rf,df_test,na.action=na.pass)

PassengerId<-pid
Survived<-res
titanic.data <- data.frame(PassengerId,Survived)
write.csv(titanic.data,file = "res.csv",row.names=FALSE)

```



